Staged Abstract Interpreters

### 2019-08-16 paper/80_related.tex
update and spaces

\paragraph{Construction of Abstract Interpreters} Abstract interpretation
was proposed as a semantics-based approach to build sound static analysis by
approximation \cite{DBLP:conf/popl/CousotC77}. As for building semantic
artifacts, the Abstracting Abstract Machines (AAM)
\cite{DBLP:journals/jfp/HornM12, DBLP:conf/icfp/HornM10} approach
shows that abstract interpreters can be derived systematically from
concrete semantic artifacts. The AAM approach is closely related to
control-flow analysis for higher-order languages
\cite{Midtgaard:2012:CAF:2187671.2187672}.  Using monads to construct
abstract interpreters is explored by
\citet{Sergey:2013:MAI:2491956.2491979} and
\citet{DBLP:journals/pacmpl/DaraisLNH17,
  Darais:2015:GTM:2814270.2814308}.  The unstaged abstract interpreter
in this paper follows the abstracting definitional interpreters
approach from \citet{DBLP:journals/pacmpl/DaraisLNH17}.  Similar to
definitional abstract interpreters,
the reconstruction of big-step abstract interpreters with delimited
continuations shown by \citet{Wei:2018:RAA:3243631.3236800},
\citet{Keidel:2018:CSP:3243631.3236767} present a modular, arrow-based
abstract interpreter that allows proof of soundness to be constructed
compositionally.

\citet{DBLP:conf/cc/CousotC02} proposed an abstract interpretation framework for
modular analysis. We borrow the notation of modular analysis for our approach.
However the staged abstract interpreter does not generate complete summaries for
modules; instead, it is able to specialize the analysis modularly. Similar, AC
is considered as an example of this kind of modular analysis \cite{DBLP:conf/cc/CousotC02}.

\paragraph{Control-flow Analysis} Our case studies and evaluation focus on
control-flow analysis for functional languages
\cite{Shivers:1991:SSC:115865.115884, Midtgaard:2012:CAF:2187671.2187672}. In
general, $k$-CFA (where $k > 0$) is considered impractical to use as a compiler
pass, due to its EXPTIME lower bound \cite{VanHorn:2008:DKC:1411204.1411243}.
However, several variants of 0CFA were developed and shown to be useful in
practice and program optimization \cite{Adams:2011:FTR:2048066.2048105,
Bergstrom:2014:PEH:2628136.2628153, ashley:practical, Reppy:2006:TCA:1159876.1159888}.

>>>>

\paragraph{Construction of Abstract Interpreters} Abstract interpretation
was proposed as a semantics-based approach to build sound static analysis by
approximation \cite{DBLP:conf/popl/CousotC77}. As for building semantic
artifacts, the Abstracting Abstract Machines (AAM)
\cite{DBLP:journals/jfp/HornM12, DBLP:conf/icfp/HornM10} approach
shows that abstract interpreters can be derived systematically from
concrete semantic artifacts. The AAM approach is closely related to
control-flow analysis for higher-order languages
\cite{Midtgaard:2012:CAF:2187671.2187672}.  Using monads to construct
abstract interpreters is explored by
\citet{Sergey:2013:MAI:2491956.2491979} and
\citet{DBLP:journals/pacmpl/DaraisLNH17,
  Darais:2015:GTM:2814270.2814308}.  The unstaged abstract interpreter
in this paper follows the abstracting definitional interpreters
approach from \citet{DBLP:journals/pacmpl/DaraisLNH17}.  Similar to
definitional abstract interpreters,
the reconstruction of big-step abstract interpreters with delimited
continuations shown by \citet{Wei:2018:RAA:3243631.3236800},
\citet{Keidel:2018:CSP:3243631.3236767} present a modular, arrow-based
abstract interpreter that allows proof of soundness to be constructed
compositionally. \citet{DBLP:conf/cc/CousotC02} proposed an abstract interpretation framework for
modular analysis. We borrow the notation of modular analysis for our approach.
However the staged abstract interpreter does not generate complete summaries for
modules; instead, it is able to specialize the analysis modularly. Similar, AC
is considered as an example of this kind of modular analysis \cite{DBLP:conf/cc/CousotC02}.

\paragraph{Control-flow Analysis} Our case studies and evaluation focus on
control-flow analysis for functional languages
\cite{Shivers:1991:SSC:115865.115884, Midtgaard:2012:CAF:2187671.2187672}. In
general, $k$-CFA (where $k > 0$) is considered impractical to use as a compiler
pass, due to its EXPTIME lower bound \cite{VanHorn:2008:DKC:1411204.1411243}.
However, several variants of 0CFA were developed and shown to be useful in
practice \cite{Adams:2011:FTR:2048066.2048105,
Bergstrom:2014:PEH:2628136.2628153, ashley:practical, Reppy:2006:TCA:1159876.1159888}.
